%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kamil K Wojcicki
\documentclass[margin,line]{resume}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Gabriel D\'iaz Iturry, PhD ~~~~~~~~~~~~~Curriculum Vitae}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}
    \vspace{2mm}
    %Oscillations Control Group                        \vspace{0mm}\\\vspace{0mm}%
    %Institute of Physics - University of S\~ao Paulo  \vspace{0mm}\\\vspace{0mm}%
    %Rua do Mat\~ao Travessa R Nr. 187 Cidade Universit\'aria, S\~ao Paulo - Brasil    \vspace{0mm}\\\vspace{0mm}% 
    e-mail: gabriel.diaz.iturry@gmail.com  \vspace{0mm}\\\vspace{0mm}%%\vspace{0mm}\\\vspace{-4.5mm}%
    github: https://github.com/gabo-di \vspace{0mm}\\\vspace{0mm}%
    Citizenship: Bolivian     ~~~~~~~~    Date of Birth: 19/11/1991   \hfill Gender: Male               \vspace{0mm}\\\vspace{4.5mm}%
    
    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}

    Chaos and Dynamical Systems, acting mainly on the following themes: diffusion in chaotic systems, nonlinear dynamics, dynamical systems, closed and open systems,  time series analysis, discrete maps, chaotic dynamics, 
    conservative and dissipative systems, time-dependent systems, Fermi acceleration, billiards,
    kicked systems, chaotic and periodic attractors, bifurcations.


    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Formal Education}

\noindent {\bf 03/2017-03/2021} -  PhD in Physics \\
           Thesis Topic:{\it Study of entropy behaviour in billiard systems.}\\
           Supervisors: { Professor Dr. Edson Denis Leonel, Professor Dr. Iber\^e Luiz Caldas}\\
           Area of Study: Nonlinear Dynamics, Chaos.\\
           Scholarships: Conselho Nacional de Desenvolvimento Cient\'ifico e Tecnol\'ogico CNPq
           Institute of Physics - University of S\~ao Paulo, S\~ao Paulo - Brasil


\noindent {\bf 03/2015-02/2017} - Master's in Physics \\
           Thesis Topic:{\it Statistical investigation and thermal properties for a 1-D impact system with dissipation.}\\
           Supervisor: { Professor Dr. Edson Denis Leonel}\\
           Area of Study: Nonlinear Dynamics and Chaos.\\
           Scholarships: Funda\c c\~ao Capes Minist\'erio da Educa\c c\~ao Brazil-CAPES DS
           State University of S\~ao Paulo - Rio Claro-SP - Brazil.

\noindent {\bf 02/2004-12/2007} - Graduation: Bachelor in Physics\\
         Thesis Topic:{\it The greatest Lyapunov Exponent in the Special Theory of Relativity: The R\"ossler case.}\\   
         Supervisors: Professor Lic. Marco A. Viscarra, Msc. Abraham C. Torrico.\\
         Universidad Mayor de San Simon - Cochabamba - Bolivia.
    
\section{\mysidestyle Languages}
\begin{itemize}
     \item {{\bf Portuguese}: Comprehends Well, Speaks Well, Writes Reasonably, Reads Well.}
     \item {\bf English}: Comprehends Well, Speaks Well, Writes Well, Reads Well.
     \item {\bf Spanish}: Comprehends Well, Speaks Well, Writes Well, Reads Well.
\end{itemize}

\section{\mysidestyle Skills}
\begin{itemize}
     \item {\bf Programming}: Fortran, Python, Julia.
     \item {\bf Software}: Wolfram's Mathematica.
\end{itemize}

    %__________________________________________________________________________________________________________________
    % Publications
    \section{\mysidestyle Publication List}
\begin{enumerate}

\item Matheus S. Palmero, Gabriel D\'ia I., Iber\^e L. Caldas, Igor M. Sokolov, {\it Sub-diffusiove behaviour in the Standard Map.} {\bf The European Physical Journal Special Topics}, p. 1-9 2021.

\item Gabriel D\'iaz I., Matheus S. Palmero, Iber\^e Luiz Caldas, Edson D. Leonel, {\it Controlling Escape in the Standard Map.} arXiv preprint arXiv:2009.11095, 2020.

\item Matheus S. Palmero, Gabriel D\'ia I., Peter V. E. McClintock, Edson D. Leonel, {\it Diffusion phenomena in a mixed phase space.} {\bf Chaos: An Interdisciplinary Journal of Nonlinear Science}, vol. 30. p. 013108, 2020.

\item Gabriel D\'iaz I., Matheus S. Palmero, Iber\^e Luiz Caldas, Edson D. Leonel, {\it Diffusion entropy analysis in billiard systems.} {\bf Physical Review E}, vol. 100, p. 042207, 2019.

\item Andr\'e L. P., Matheus S. Palmero, Gabriel D\'iaz I., Carl P. Dettmann, Iber\^e L. Caldas, Edson D. Leonel, {\it Investigation of stickiness influence in the anomalous transport and diffusion for a non-disipative Fermi-Ulam model.} {\bf Communications in Nonlinear Science and Numerical Simulation}, vol. 55, p. 225-236, 2018.

\item Gabriel D\'iaz I., Makoto Yoshida, Edson D. Leonel, {\it A Monte Carlo approach for the bouncer model.} {\bf Physics Letters A}, vol. 381, p. 3636-3640, 2017.

\item Gabriel D\'iaz I. Andr\'e L. P. Livorati, Edson D. Leonel, {\it Statistical investigation and thermal properties for a 1-D impact system with dissipation.} {\bf Physics Letters A}, vol. 380, p. 1830-1838, 2016.
\end{enumerate}

    
      \section{\mysidestyle Conferences,Workshops and Meeting}  
    
    \begin{enumerate}
\item  Hands-On Research in Complex Systems School, ICTP - Trieste - Italy. (2018)     
\item  International Conference on Transport and Diffusion in Dynamical Systems, S\~ao Carlos - S\~ao Paulo, Brazil. (2016).

\end{enumerate}


%______________________________________________________________________________________________________________________
\section{\mysidestyle Referees} 


\begin{itemize}
    \item {\bf Prof. Dr. Edson Denis Leonel }  \\  Departamento de F\'isica  \\ Universidade Estadual Paulista Campus de Rio Claro \\Av. 24A, 1515 - Bela Vista - CEP 13.506-700 - Rio Claro - S\~ao Paulo - Brazil \\ Phone: +55(19)3557 3654 - Fax: +55(19) 3526 9181\\ e-mail: edson-denis.leonel@unesp.br \
    \item {\bf Prof. Dr, Iber\^e Luiz Caldas} \\ Departamento de F\'isica Aplicada \\ Instituto de F\'isica, Universidade de S\~ao Paulo
    \\ Rua do Mat\~ao Travessa R Nr. 187 Cidade Universit\'aria, S\~ao Paulo - Brasil \\ Phone: +55 (11) 3091-6914\\ e-mail: ibere@if.usp.br \ 
    \item {\bf Prof. Dr, Luiz Antonio Barreiro} \\ Departamento de F\'isica \\ Universidade Estadual Paulista Campus de Rio Claro \\Av. 24A, 1515 - Bela Vista - CEP 13.506-700 - Rio Claro - S\~ao Paulo - Brazil \\ Phone: +55(19) 3526 9186\\ e-mail: luiz.a.barreiro@unesp.br \
    
\end{itemize}
%\end{thebibliography}


%\begin{tabular}{@{}p{6cm}p{6cm}}
%\textbf{Dr Conrad Sanderson}            &  \textbf{Mr Sean Loye}                    \\
%Researcher                              &  Systems Engineer                         \\
%National ICT Australia                  &  Hewlett Packard                          \\
%St Lucia, Queensland, Australia         &  Milton, Queensland, Australia            \\
%phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
%e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
%\end{tabular}



%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

